---
title: "Exam 1 Results and Statistics"
output: html_document
---

```{r Installing Packages, include = FALSE}
options(stringsAsFactors = FALSE)
install.packages("here", repos = "http://cran.us.r-project.org")
library(here)
install.packages("xts", repos = "http://cran.us.r-project.org")
library(xts)
install.packages("zoo", repos = "http://cran.us.r-project.org")
library(zoo)
install.packages("ggplot2", repos = "http://cran.us.r-project.org")
library(ggplot2)
```

```{r IMPORT: Grades, include = FALSE}
data_cnv <- read.csv(here("./src/routes/(full-website)/exam-1/Data/Gradebook_Sep_20.csv")) # nolint
data_cnv <- data_cnv[-1, ] # Removing Possible Points row
data_cnv <- data_cnv[-61, ] # Removing Test Student
data_cnv <- data_cnv[, -2] # Removing ID column
data_cnv <- data_cnv[-c(3:7)]
data_cnv <- data_cnv[-c(5:6)]
data_cnv <- data_cnv[-6]
data_cnv <- data_cnv[-c(7:ncol(data_cnv))]

# Calculating bonus points
for (i in nrow(data_cnv):1) {
    data_cnv[i, 7] <- (data_cnv[i, 3] + data_cnv[i, 4] + data_cnv[i, 5] + data_cnv[i, 6])
}
data_cnv <- data_cnv[-c(3:6)]
colnames(data_cnv) <- c("Name", "UIN", "EC")
rownames(data_cnv) <- c(1:60)
```

```{r CREATE: Grades, include = FALSE}
data_cnv[1, c(4:12)] <- c(2, 2, 4, 2, 2, 0, 2, 2.5, 0)
data_cnv[2, c(4:12)] <- c(2, 0, 4, 2, 0, 1, 1, 0, 0)
data_cnv[3, c(4:12)] <- c(2, 0, 2, 0, 0, 2, 2, 0, 0)
data_cnv[4, c(4:12)] <- c(2, 0, 2, 0, 3, 1, 3, 0, 0)
data_cnv[5, c(4:12)] <- c(0, 2, 2, 0, 0, 0, 2, 0, 0)
data_cnv[6, c(4:12)] <- c(8, 4, 6, 0, 2, 2, 7, 2.5, 0)
data_cnv[7, c(4:12)] <- c(0, 6, 2, 0, 0, 1, 5, 5, 0)
data_cnv[8, c(4:12)] <- c(4, 4, 0, 0, 8, 1, 6, 0, 0)
data_cnv[9, c(4:12)] <- c(2, 0, 2, 0, 0, 1, 2, 2.5, 0)
data_cnv[10, c(4:12)] <- c(4, 0, 2, 2, 3, 0, 5, 5, 0)
data_cnv[11, c(4:12)] <- c(2, 4, 8, 0, 2, 0, 5, 0, 5)
data_cnv[12, c(4:12)] <- c(4, 2, 2, 0, 5, 1, 3, 2.5, 0)
data_cnv[13, c(4:12)] <- c(2, 4, 4, 2, 7, 1, 3, 0, 0)
data_cnv[14, c(4:12)] <- c(2, 2, 2, 0, 0, 0, 2, 0, 5)
data_cnv[15, c(4:12)] <- c(2, 6, 4, 2, 4, 1, 5, 2.5, 0)
data_cnv[16, c(4:12)] <- c(2, 2, 2, 0, 2, 1, 4, 2.5, 0)
data_cnv[17, c(4:12)] <- c(4, 4, 6, 0, 0, 2, 3, 2.5, 0)
data_cnv[18, c(4:12)] <- c(4, 0, 2, 0, 0, 1, 4, 0, 0)
data_cnv[19, c(4:12)] <- c(4, 2, 4, 2, 2, 1, 1, 0, 5)
data_cnv[20, c(4:12)] <- c(4, 2, 2, 6, 2, 1, 5, 5, 0)
data_cnv[21, c(4:12)] <- c(2, 0, 2, 0, 6, 1, 3, 2.5, 0)
data_cnv[22, c(4:12)] <- c(2, 2, 4, 2, 4, 1, 5, 0, 0)
# data_cnv[23, c(4:12)] <- c()
data_cnv[24, c(4:12)] <- c(2, 2, 0, 0, 0, 1, 4, 2.5, 0)
data_cnv[25, c(4:12)] <- c(4, 4, 4, 2, 4, 1, 3, 0, 0)
data_cnv[26, c(4:12)] <- c(6, 2, 4, 0, 3, 1, 5, 2.5, 0)
data_cnv[27, c(4:12)] <- c(2, 4, 0, 2, 3, 1, 4, 0, 0)
data_cnv[28, c(4:12)] <- c(0, 0, 0, 0, 4, 1, 4, 2.5, 0)
data_cnv[29, c(4:12)] <- c(2, 2, 2, 4, 2, 1, 3, 0, 0)
data_cnv[30, c(4:12)] <- c(0, 4, 2, 0, 0, 0, 2, 0, 5)
data_cnv[31, c(4:12)] <- c(2, 2, 2, 0, 0, 1, 1, 2.5, 0)
data_cnv[32, c(4:12)] <- c(2, 6, 2, 2, 0, 1, 3, 0, 5)
data_cnv[33, c(4:12)] <- c(4, 4, 2, 0, 4, 1, 4, 2.5, 0)
data_cnv[34, c(4:12)] <- c(2, 0, 4, 0, 3, 1, 3, 0, 0)
data_cnv[35, c(4:12)] <- c(0, 0, 2, 0, 2, 1, 2, 1, 0)
data_cnv[36, c(4:12)] <- c(4, 4, 5, 4, 4, 1, 3, 0, 5)
data_cnv[37, c(4:12)] <- c(2, 0, 2, 0, 2, 0, 4, 0, 0)
data_cnv[38, c(4:12)] <- c(0, 0, 2, 0, 3, 0, 1, 0, 0)
data_cnv[39, c(4:12)] <- c(2, 4, 4, 0, 0, 6, 4, 2.5, 0)
data_cnv[40, c(4:12)] <- c(2, 8, 2, 0, 2, 0, 2, 0, 0)
data_cnv[41, c(4:12)] <- c(0, 4, 2, 0, 8, 1, 5, 0, 0)
data_cnv[42, c(4:12)] <- c(4, 8, 0, 0, 5, 2, 5, 5, 0)
data_cnv[43, c(4:12)] <- c(0, 4, 2, 0, 2, 0, 1, 2.5, 0)
data_cnv[44, c(4:12)] <- c(0, 4, 4, 2, 2, 1, 5, 0, 0)
data_cnv[45, c(4:12)] <- c(2, 2, 4, 0, 3, 1, 2, 0, 0)
data_cnv[46, c(4:12)] <- c(0, 4, 2, 4, 4, 1, 5, 0, 0)
data_cnv[47, c(4:12)] <- c(6, 0, 4, 0, 2, 1, 2, 0, 5)
data_cnv[48, c(4:12)] <- c(2, 6, 2, 0, 0, 1, 2, 2.5, 0)
data_cnv[49, c(4:12)] <- c(4, 2, 2, 0, 3, 1, 2, 0, 5)
data_cnv[50, c(4:12)] <- c(0, 0, 2, 0, 0, 1, 2, 0, 0)
data_cnv[51, c(4:12)] <- c(0, 4, 6, 2, 2, 0, 5, 5, 0)
data_cnv[52, c(4:12)] <- c(2, 2, 2, 0, 0, 0, 4, 1, 0)
data_cnv[53, c(4:12)] <- c(2, 8, 4, 0, 2, 1, 5, 0, 5)
data_cnv[54, c(4:12)] <- c(4, 8, 2, 2, 3, 1, 3, 0, 0)
data_cnv[55, c(4:12)] <- c(0, 2, 2, 4, 0, 1, 4, 0, 0)
data_cnv[56, c(4:12)] <- c(2, 4, 2, 0, 3, 1, 1, 0, 5)
data_cnv[57, c(4:12)] <- c(0, 2, 6, 0, 0, 1, 2, 0, 0)
data_cnv[58, c(4:12)] <- c(0, 4, 4, 0, 4, 2, 5, 3.5, 0)
data_cnv[59, c(4:12)] <- c(0, 8, 6, 0, 3, 2, 4, 2.5, 0)
data_cnv[60, c(4:12)] <- c(0, 2, 2, 0, 0, 1, 2, 2.5, 0)

for (i in nrow(data_cnv):1) {
    data_cnv[i, 13] <- (100 - data_cnv[i, 4] - data_cnv[i, 5] - data_cnv[i, 6] - data_cnv[i, 7] - data_cnv[i, 8] - data_cnv[i, 9] - data_cnv[i, 10] - data_cnv[i, 11] + data_cnv[i, 12])
    data_cnv[i, 14] <- (data_cnv[i, 3] + 100 - data_cnv[i, 4] - data_cnv[i, 5] - data_cnv[i, 6] - data_cnv[i, 7] - data_cnv[i, 8] - data_cnv[i, 9] - data_cnv[i, 10] - data_cnv[i, 11] + data_cnv[i, 12])
}

colnames(data_cnv) <- c("Name", "UIN", "EC", "P1", "P2", "P3", "P4", "P5", "P6", "P7", "P8", "Bonus", "Raw", "Final")

# View(data_cnv)
```

```{r CREATE: Missed Questions, include = FALSE}
data_mis <- matrix(NA, ncol = 1, nrow = 52)

# Page 1 True/False
data_mis[1, ] <- 32
data_mis[2, ] <- 11
data_mis[3, ] <- 0
data_mis[4, ] <- 5
data_mis[5, ] <- 12
data_mis[6, ] <- 22

# Page 2 True/False
data_mis[7, ] <- 20
data_mis[8, ] <- 0
data_mis[9, ] <- 18
data_mis[10, ] <- 13
data_mis[11, ] <- 12
data_mis[12, ] <- 11
data_mis[13, ] <- 2
data_mis[14, ] <- 9
data_mis[15, ] <- 1

# Page 3 Multiple Choice
data_mis[16, ] <- 1
data_mis[17, ] <- 13
data_mis[18, ] <- 12
data_mis[19, ] <- 15
data_mis[20, ] <- 45

# Page 4 Multiple Choice
data_mis[21, ] <- 6
data_mis[22, ] <- 4
data_mis[23, ] <- 2
data_mis[24, ] <- 10
data_mis[25, ] <- 2

# Page 5 Matching Part 1
data_mis[26, ] <- 0
data_mis[27, ] <- 0
data_mis[28, ] <- 3
data_mis[29, ] <- 0
data_mis[30, ] <- 0
data_mis[31, ] <- 0
data_mis[32, ] <- 0
data_mis[33, ] <- 3
data_mis[34, ] <- 0

# Page 5 Matching Part 2
data_mis[35, ] <- 4
data_mis[36, ] <- 24
data_mis[37, ] <- 8
data_mis[38, ] <- 2
data_mis[39, ] <- 27
data_mis[40, ] <- 17
data_mis[41, ] <- 24
data_mis[42, ] <- 17
data_mis[43, ] <- 3
data_mis[44, ] <- 1

# The following sections measure instances of partial/no credit.

# Page 6 Cost Evaluation
data_mis[45, ] <- 1
data_mis[46, ] <- 2
data_mis[47, ] <- 45

# Page 7 Adverse Selection
data_mis[48, ] <- 49
data_mis[49, ] <- 43
data_mis[50, ] <- 43

# Page 8 Essay & Bonus
data_mis[51, ] <- 26
data_mis[52, ] <- 48
```

```{r CREATE: Turn-in Times, include = FALSE}
data_all <- data_cnv[-c(2:12)]

data_all[1, 4] <- 69 # nice
data_all[2, 4] <- 72
data_all[3, 4] <- 45
data_all[4, 4] <- 78
data_all[5, 4] <- 69
data_all[6, 4] <- 67
data_all[7, 4] <- 39
data_all[8, 4] <- 59
data_all[9, 4] <- 79
data_all[10, 4] <- 43
data_all[11, 4] <- 55
data_all[12, 4] <- 71
data_all[13, 4] <- 89
data_all[14, 4] <- 73
data_all[15, 4] <- 55
data_all[16, 4] <- 84
data_all[17, 4] <- 50
data_all[18, 4] <- 89
data_all[19, 4] <- 51
data_all[20, 4] <- 46
data_all[21, 4] <- 75
data_all[22, 4] <- 72
# data_all[23, 4] <- didn't take exam
data_all[24, 4] <- 89
data_all[25, 4] <- 67
data_all[26, 4] <- 80
data_all[27, 4] <- 83
data_all[28, 4] <- 36
data_all[29, 4] <- 70
data_all[30, 4] <- 82
data_all[31, 4] <- 56
data_all[32, 4] <- 82
# data_all[33, 4] <- not collected
data_all[34, 4] <- 51
data_all[35, 4] <- 60
data_all[36, 4] <- 58
data_all[37, 4] <- 74
data_all[38, 4] <- 82
data_all[39, 4] <- 45
data_all[40, 4] <- 76
data_all[41, 4] <- 82
data_all[42, 4] <- 53
data_all[43, 4] <- 61
data_all[44, 4] <- 89
data_all[45, 4] <- 89
data_all[46, 4] <- 89
data_all[47, 4] <- 66
data_all[48, 4] <- 85
data_all[49, 4] <- 41
data_all[50, 4] <- 59
data_all[51, 4] <- 82
data_all[52, 4] <- 77
data_all[53, 4] <- 80
data_all[54, 4] <- 85
data_all[55, 4] <- 87
data_all[56, 4] <- 50
data_all[57, 4] <- 67
data_all[58, 4] <- 42
data_all[59, 4] <- 79
data_all[60, 4] <- 53

# View(data_all)
```

## Descriptive Statistics

```{r VALUES: Descriptive Statistics, include = FALSE}
val_raw_avg <- round(colMeans(data_all[2], na.rm = TRUE), digits = 1)
val_raw_obs <- round(sum(!is.na(data_all[2])), digits = 1)
val_fin_avg <- round(colMeans(data_all[3], na.rm = TRUE), digits = 1)
val_fin_obs <- round(sum(!is.na(data_all[3])), digits = 1)
```

The first exam was taken by `r val_fin_obs` students. The raw score average (without extra credit) was `r val_raw_avg` and the final score average (with extra credit) was `r val_fin_avg`.

The figure below plots the grade distribution for the class. The raw scores are plotted in <b><span style = "color: #000000">black</span></b> and the final scores are plotted in <b><span style = "color: #f3f3f3">gray</span></b>.

```{r PLOT: Grade Distribution, include = TRUE, echo = FALSE}
# plot_grd_dis_raw <- data_all[2]

# hist(data_all[2], main = "Grade Distribution", xlab = "Grade", ylab = "Frequency", col = "blue", breaks = 0, xlim = c(0, 100))


# ggplot(plot_grd_dis, aes(x = frequency(`Raw`))) +
#     geom_bar()

# ggplot(plot_grd_dis, aes(x = plot_grd_dis[1], y = plot_grd_dis[2], size = 2) +
#     geom_point(color = color_gini) +
#     ggtitle("Grade Distribution") +
#     ggeasy::easy_center_title() +
#     xlim(0, 100) +
#     ylim(0, 100) +
#     xlab("R&D Expenditure") +
#     ylab("Gini Index") +
#     geom_smooth(
#         aes(x = plot_grd_dis[1], y = plot_grd_dis[2]),
#         method = lm, se = TRUE,
#         color = color_trendline
#     ) +
#     theme(aspect.ratio = 2.625 / 3.75))
```

## Most Missed Questions

Below is a bar graph depicting the number of instances a question was missed/not asnwered fully correctly. The bars are arranged from left to right by question order. Each section of the exam has its own color:

* The True/False questions are plotted in <b><span style = "color: #bf1818">red</span></b>.
* The Multiple Choice questions are plotted in <b><span style = "color: #e4770b">orange</span></b>.
* The Matching questions are plotted in <b><span style = "color: #ffe600">yellow</span></b>.
* The Cost Evaluation problem is plotted in <b><span style = "color: #1c7a1c">green</span></b>.
* The Adverse Selection problem is plotted in <b><span style = "color: #348bcd">blue</span></b>.
* The Essay and Bonus questions are plotted in <b><span style = "color: #6a308e">purple</span></b>.
* Questions that have been voided are plotted in <b><span style = "color: #868686">gray</span></b>.

```{r PLOT: Missed Questions, include = TRUE, echo = FALSE}
# Creating plot
plot_data_mis <- data.frame(
    qID = c(1:52),
    mis = data_mis[, 1],
    col = c(
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#868686",
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#bf1818",
        "#e4770b",
        "#e4770b",
        "#e4770b",
        "#e4770b",
        "#e4770b",
        "#e4770b",
        "#e4770b",
        "#e4770b",
        "#e4770b",
        "#e4770b",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#ffe600",
        "#1c7a1c",
        "#1c7a1c",
        "#1c7a1c",
        "#348bcd",
        "#348bcd",
        "#348bcd",
        "#6a308e",
        "#6a308e"
    )
)

ggplot(plot_data_mis, aes(x = factor(plot_data_mis[, 1]), y = factor(plot_data_mis[, 2]), fill = factor(plot_data_mis[, 1]))) +
    geom_bar(stat = "identity") +
    geom_hline(yintercept = 30) +
    ggtitle("Instances of No or Partial Credit") +
    ggeasy::easy_center_title() +
    theme(aspect.ratio = 5.25 / 7.5, legend.position = "none") +
    scale_fill_manual(values = plot_data_mis[, 3]) +
    xlab("Question") +
    ylab("Number of Instances")
```